Are you normal? A new projection pursuit index to assess a sample against a multivariate null distribution

### 2024-06-27 paper.qmd
fixing derivation

$$(\mathbfit{x}-\mathbfit{\mu}) \Sigma^{-1}(\mathbfit{x}-\mathbfit{\mu})^T = 2 (\mathbfit{x}-\mathbfit{\mu}) \Sigma^{-1} = 2\mathbfit{s}P^T
$$

@@

We call points in the projection that are on the curve $\mathbfit{y}$. From this we can compute the analog equation for the projection as

>>>>

$$\nabla (\mathbfit{x}-\mathbfit{\mu}) \Sigma^{-1}(\mathbfit{x}-\mathbfit{\mu})^T = 2 (\mathbfit{x}-\mathbfit{\mu}) \Sigma^{-1} = 2\mathbfit{s}P^T
$$

@@

We call points in the projection that are on the curve \(\mathbfit{y}\), so that \(\mathbfit{y} = \mathbfit{x}P\) for \(\mathbfit{x}\) on the \pD{} curve. Then \(\mathbfit{y} - \mathbfit{\mu}_p = (\mathbfit{x} - \mathbfit{\mu})P = \mathbfit{s} P^T \Sigma P\), where \(\mathbfit{\mu}_p = \mathbfit{\mu} P\) is the projected mean. We then substitute \((\mathbfit{y} - \mathbfit{\mu}_p) (P^T \Sigma P)^{-1}\) for \(\mathbfit{s}\) in the previous equation. From this we can compute the analog equation for the projection as
